Automated Synthesis of State-Space Digital Systems

### 2017-01-16 cav2017/cav2017.tex
minor changes

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\ref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers creating a feedback loop in the form
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k\ \ :\ \ \mat{K}_d \in \mathbb{R}^{m \times o}.
\end{equation}
%
where $\mat{K}_d$ are the feedback coefficients.
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}

@@

>>>>

%-------------------------------
\section{Preliminaries}
\label{sec:preliminaries}
%-------------------------------

%-------------------------------
\subsection{State-space representation of dynamical systems}
\label{ssec:ssrepresentation}
%-------------------------------

In this study, we focus on Cyber-Physical Systems with continuous 
dynamical plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%

%-------------------------------
\subsection{State feedback control}
\label{ssec:statefeedbackcontrol}
%-------------------------------

Feedback control is usually employed to modify and control the properties and behaviors of process and systems, reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
%
\begin{equation}
\vec{u}_k=\vec{r}_{k}-\mat{K}\vec{x}_k.
\end{equation}
%
where $\mat{K} \in \mathbb{R}^{m \times o}$ is the state feedback gain matrix.
%
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}
\commentib{What is S?}

@@

%-------------------------------
\subsection{Stability of closed-loop systems}
\label{ssec:stability}
%-------------------------------

%-------------------------------
\subsection{Quantization error in digital controllers of Cyber-Physical Systems}
\label{ssec:quantizationerror}
%-------------------------------

%-------------------------------
\subsection{Safety specifications for Cyber-Physical Systems}
\label{ssec:safety}
%-------------------------------
